Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications

### 2017-05-25 automatica/automatica.tex
automatica structure

@@

>>>>

{\color{blue}[IB:] In my opinion, the subsections \ref{ssec:statefeedbackcontrol}, \ref{ssec:ssrepresentation}, are \ref{ssec:stability} are useless for the Automatica audience. In addition, i guess that all the subsections~\ref{ssec:ssrepresentation}-\ref{ssec:performance} should be erased and a new section about formal specification of transient and stability specifications can be created.}

%-------------------------------
\subsection{Notation} 
\label{ssec:notation}
%-------------------------------

%-------------------------------
\subsection{Counterexample Guided Inductive Synthesis} 
\label{ssec:cegis}
%-------------------------------

%-------------------------------
\subsubsection{CEGIS of digital controllers} 
\label{sssec:cegisdig}
%-------------------------------

%-------------------------------
\subsubsection{Naive approach} 
\label{sssec:naive}
%-------------------------------

%-------------------------------
\subsubsection{Abstraction-based CEGIS} 
\label{sssec:abstraction}
%-------------------------------

@@

%-------------------------------
\section{Formal specification of control systems properties} 
\label{sec:specification}
%-------------------------------

%-------------------------------
\subsection{Formal specification of stability} 
\label{ssec:stabspecification}
%-------------------------------

%-------------------------------
\subsection{Formal specification of safety} 
\label{ssec:safespecification}
%-------------------------------

%-------------------------------
\subsection{Formal specification of transient response} 
\label{ssec:transientspecification}
%-------------------------------

%-------------------------------
\section{CEGIS of digital control system with transient specifications}
\label{sec:method}
%-------------------------------

%-------------------------------
\subsection{Synthesis in frequency domain}
\label{ssec:frequencycegis}
%-------------------------------

%-------------------------------
\subsection{Synthesis of state feedback controllers}
\label{ssec:sscegis}
%-------------------------------

%-------------------------------
\subsection{Synthesis of state observers}
\label{ssec:sobsvcegis}
%-------------------------------
